\documentclass{article}
\usepackage{a4wide}
\title{\emph{ 10 Data mangement tools  }}
\author{Daniel Ocampo}
\begin{document}
\maketitle 
\linespread{1.0}\selectfont

\begin{enumerate}
\item SQL 

SQL allows users to insert, delete,update, create, and drop. which according to the site that I just finished reading those are the necessary things that are needed to make a database. Based on my research I found a couple of things that are useful in terms of SQL. There are two tools that I found.

\begin{itemize}
\item MySQL
\item SQLITE



\end{itemize} 

\item ScalaQuery

This is simialr to SQL but written in scala. The diffrence between scalaQuery and SQL is that Scala has static types, and can be checked by the scala compiler.     

\item Hibernate Query Language 

Also simialr to sql it has  simialr atributes to sql but accoriding to my research it is more object oritented language. 


\item Language-Integrated Query

From what I got from the site is that it seems to be just like SQL but it is intergrated with c\#. not sure what exactly differentiates them from each other.


\item NoSQL



NoSQL is being used for big Data, after the creation of web 2.0 compines according to the site that I found online. It also stated that it has simplistic approach although to me is still seems complicated. ( still learning about databases)

\item phpmyadmin
Gives the user the a abilty to make a localhost server and allow it input data and converting the data into sql using the code. which is something that I listed in the previous example. It also alows a localhost for website development. 

\item  Adminer

Adminer according to wikipedia is a web database, it has the ability to support many languages in the sense of communitction of nationalities. 

\item AQT

one of the neat things that I found out about this one is that is allows for scrips to be used. 

\item DaDaBIK

According to wikipedia one of the main features of this tool is that it, "checks for possible duplication  during insertions, authentication, authoruzation restrictions on view/update/delete and e-mail notices."
\item Database Deployment Manager

Database Design and  Data Modeling. It is also object oriented which is something I put down because not sure what they mean by that. Hopefully I can get feedback on that. 



\end{enumerate}







\end{document}



